Defending Byzantine Attacks in Ensemble Federated Learning: A Reputation-based Phishing Approach

### 2022-01-21 Manuscript/FLPhish(Trans).tex
图的引用的修改

\markboth{Journal of \LaTeX\ Class Files,~Vol.~14, No.~8, August~2015}%
{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for IEEE Journals}

@@

    \subsubsection{\ul{Performance Comparison with Different Fractions of Byzantine Clients}} Different fractions of Byzantine clients are taken into account as well. Figure. \ref{fig_table_byzantines_untargeted} shows that the accuracy for FedAvg, Median and Trimmed Mean begins to fall rapidly when the Byzantine portion reaches nearly 50\%. Furthermore, FedAvg, Median, and Trimmed Mean perform extremely invalidly (the accuracy falls below 1\%) when encountered with high fractions of Byzantine attackers. In comparison, FLPhish($\tau$) and FLPhish(weight)'s performance under various thresholds maintain a high level of performance as the portion grows. Both FLPhish($\tau$) and FLPhish(weight) effectively detect Byzantine clients and accurately discard them from the aggregation process. The global model can be successfully trained without the involvement of Byzantine clients during the aggregation procedures. Furthermore, the data show that FLPhish($\tau$=0.1) performs worse than the other two. This is since the threshold=0.1 is far too low to adequately detect Byzantine clients. Though the Byzantine attackers try to make the right predictions of the public dataset and then send the opposite wrong predictions to the FL server. But they also make wrong predictions first and coincidentally transfer the opposite right predictions to the FL server. Thus the reputation values of some Byzantine clients, in particular, can exceed 0.1. It indicates that if the threshold is not well set, Byzantine clients can avoid being detected by FLPhish($\tau$=0.5). As the fractions of Byzantine clients go over the threshold of 50\%, the harm brought by untargeted Byzantine attacks increase rapidly for they outnumber the fractions of the benign clients. In the meantime, FLPhish(weight) shows stable performance whenever the fractions of Byzantine clients are.

>>>>

\markboth{IEEE TRANSACTIONS ON INFORMATION FORENSICS AND SECURITY}%
{Wang \MakeLowercase{\textit{et al.}}: Defending Byzantine Attacks in Ensemble Federated Learning: A Reputation-based Phishing Approach}

@@

    \subsubsection{\ul{Performance Comparison with Different Fractions of Byzantine Clients}} Different fractions of Byzantine clients are taken into account as well. Figure. \ref{fig_table_byzantines_untargeted} shows that the accuracy for FedAvg, Median and Trimmed Mean begins to fall rapidly when the Byzantine portion reaches nearly 50\%. Furthermore, FedAvg, Median, and Trimmed Mean perform extremely invalidly (the accuracy falls below 1\%) when encountered with high fractions of Byzantine attackers. In comparison, FLPhish($\tau$) and FLPhish(weight)'s performance under various thresholds maintain a high level of performance as the portion grows. Both FLPhish($\tau$) and FLPhish(weight) effectively detect Byzantine clients and accurately discard them from the aggregation process. The global model can be successfully trained without the involvement of Byzantine clients during the aggregation procedures. Furthermore, the data show that FLPhish($\tau$=0.1) performs worse than the other two. This is since the threshold=0.1 is far too low to adequately detect Byzantine clients. Though the Byzantine attackers try to make the right predictions of the public dataset and then send the opposite wrong predictions to the FL server. But they also make wrong predictions first and coincidentally transfer the opposite right predictions to the FL server. Thus the reputation values of some Byzantine clients, in particular, can exceed 0.1. It indicates that if the threshold is not well set, Byzantine clients can avoid being detected by FLPhish($\tau$). As the fractions of Byzantine clients go over the threshold of 50\%, the harm brought by untargeted Byzantine attacks increase rapidly for they outnumber the fractions of the benign clients. In the meantime, FLPhish(weight) shows stable performance whenever the fractions of Byzantine clients are.
